---
title: "README: Employment Data Set"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
---

```{r, include = FALSE}
###########################
# STYLE EDITS: IGNORE THIS
###########################
# normally you'll want to include this with the libraries at the beginning of your document
knitr::opts_chunk$set(message = FALSE) # include this if you don't want markdown to knit messages
knitr::opts_chunk$set(warning = FALSE) # include this if you don't want markdown to knit warnings
```

We will work with a data set on employment rates and related indicators for the 28 nations in the European Union.  This data set is a subset of the Organisation for Economic Co-operation and Development (OECD)'s data set found at 
https://stats.oecd.org/. Specifically, you could find the original data by clicking Labour > World Indicators of Skills for Employment.

# Read in data

To read in the data, type the following:

```{r}
library(tidyverse)

employment <- read_csv("https://raw.githubusercontent.com/RobinMDunn/stat315_summer19_data/master/employment/employment.csv")
```


# Variables

Observe that the data set has 252 rows and 11 columns.

Each row contains the following information on a single nation in a single year:

| Column Name         |  Description |
|--------------|-------------------------------------|
country | country (one of 28 European Union nations)
year  | year (between 2003 and 2011)
empl_agri | percent of labor force employed in agriculture sector
empl_indu | percent of labor force employed in industry
empl_serv | percent of labor force employed in service sector
self_empl | percent of labor force that is self-employed
unemp_youth | youth unemployment percentage
unemp_adult | adult unemployment percentage
urban | percent of population living in urban areas
mobile | number of mobile phones per 100 inhabitants
internet | percent of households with access to Internet
