---
title: "README: University Data Set"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
---

```{r, include = FALSE}
###########################
# STYLE EDITS: IGNORE THIS
###########################
# normally you'll want to include this with the libraries at the beginning of your document
knitr::opts_chunk$set(message = FALSE) # include this if you don't want markdown to knit messages
knitr::opts_chunk$set(warning = FALSE) # include this if you don't want markdown to knit warnings
```

This data set is a modified version of the University data set found at 
http://archive.ics.uci.edu/ml/datasets/university. 

The data were provided by Steve Souders.

The information below will be repeated on the exam.

# Read in data

To read in the data, type the following:

```{r}
library(tidyverse)

university <- read_csv("https://raw.githubusercontent.com/RobinMDunn/stat315_summer19_data/master/university/university.csv")
```

Use the following code to re-order the categories of students and apps:

```{r}
university <- university %>%
  mutate(students = factor(students,
                           levels = c("<5", "5-10", "10-15", "15-20", "20+"),
                           labels = c("<5", "5-10", "10-15", "15-20", "20+")),
         apps = factor(apps,
                       levels = c("<4", "4-7", "7-10", "10-13", "13-17", "17+"),
                       labels = c("<4", "4-7", "7-10", "10-13", "13-17", "17+")))
```

# Variables

Observe that the data set has 122 rows and 12 columns.

Each row contains the following information on a single university:

| Column Name         |  Description |
|--------------|-------------------------------------|
location | suburban, urban, small-city, or small-town setting 
control  | public or private university 
students | number of students (thousands) 
male_female | number of male students divided by number of female students
student_fac | number of students divided by number of faculty members
SAT_verbal | median SAT verbal score of students
SAT_math | median SAT math score of students
apps | number of applications received by university (thousands)
percent_admit | percentage of applicants who are admitted
academics | scale from 1-5 (discrete, categorical) rating the quality of academics
social | scale from 1-5 rating the quality of university social life
quality_life | scale from 1-5 rating the overall quality of life at the university
